Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-11 ms.tex
more clean-up of CO subtraction discussion

To correct for molecular emission, we employed the \PLANCK~Type 3 CO data 
product, which boasts the highest S/N among the available full-sky CO 
maps based on the \PLANCK~HFI and Low Frequency Instrument (LFI) data 
\citep{planckco}. The native angular resolution of the Type 3 CO map is 5.5$'$.
We therefore began by smoothing the raw Type 3 CO map to $6.1'$, to match the 
PSF of the smoothed \PLANCK~intensity maps we wish to correct for molecular 
emission (for our full-resolution two-parameter fits, these are 217 GHz and 353
GHz).

We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO map 
before subtracting it from the \PLANCK~intensity maps, which have native units 
of $K_{CMB}$ at the frequencies of interest. The Type 3 CO map is provided in 
units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. To convert this quantity 
to $K_{CMB}$, we assume that all of the CO emission arises from the $^{12}$CO 
isotope, and derived the \PLANCK-observed CO intensity in units of $K_{CMB}$ as
follows:

@@

% We did not attempt to correct for higher J CO transitions beyond J=3->2

>>>>

To correct for molecular emission, we employ the \PLANCK~Type 3 CO data 
product, which boasts the highest S/N among the available full-sky CO maps 
based on the \PLANCK~HFI and Low Frequency Instrument (LFI) data 
\citep{planckco}. The native angular resolution of the Type 3 CO map is 5.5$'$.
We therefore begin by smoothing the raw Type 3 CO map to match the PSF of the 
smoothed \PLANCK~intensity maps we wish to correct for molecular emission.

We must apply the appropriate unit conversions to the Type 3 CO map before 
subtracting it from the \PLANCK~intensity maps, which have native units of 
$K_{CMB}$ at the frequencies of interest. The Type 3 CO map is provided in 
units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. To convert this quantity 
to $K_{CMB}$, we assume that all of the CO emission arises from the $^{12}$CO 
isotope, and derive the \PLANCK-observed CO intensity in units of $K_{CMB}$ as
follows:

@@
